First Season MWA EoR Power Spectrum Results at Redshift 7

### 2016-05-19 ms.tex
added rts-chips data to limit table, switched to deluxetable

\begin{table}
\begin{center}
\caption[EoR power spectrum limits]{Upper limits on the EoR power spectrum for our three 
sub-bands and two polarizations. Upper limits, $\Delta^2_{\text{UL}}$, are at 97.7\% 
confidence level.
\label{tbl:limits}
}
\begin{tabular}{ccccc}
\tableline\tableline
Sub-band & $z_0$ & Polarization & $k$ (h Mpc$^{-1}$) & $\Delta^2_{\text{UL}}$ (mK$^2$) \\
\tableline
Low & 7.1 & E-W & 0.231 & 3.67 $\times 10^4$\\
Low & 7.1 & N-S & 0.27 & 2.70 $\times 10^4$\\
Mid & 6.8 & E-W & 0.24 & 3.56 $\times 10^4$\\
Mid & 6.8 & N-S & 0.24 & 3.02 $\times 10^4$\\
High & 6.5 & E-W & 0.20 & 4.70 $\times 10^4$\\
High & 6.5 & N-S & 0.24 & 3.22 $\times 10^4$\\
\tableline
\end{tabular}
\end{center}
\end{table}

>>>>

\begin{deluxetable}{ccccccc}
\tabletypesize{\footnotesize}
%\tablecolumns{7}
\tablewidth{\columnwidth}
\tablecaption{Upper limits on the EoR power spectrum for our three 
sub-bands and two polarizations. Upper limits, $\Delta^2_{\text{UL}}$, are at 97.7\% 
confidence level. Cosmological wavenumbers, $k$, are in units of h~Mpc$^{-1}$ and upper limits are in units of mK$^2$. The last two columns, RTS-CHIPS, are produced from the reference pipeline which is discussed in Section~\ref{subsec:ref_pipe}.
\label{tbl:limits}
}
\tablehead{
& & & \multicolumn{2}{c}{FHD-\eppsilon} & \multicolumn{2}{c}{RTS-CHIPS} \\
Sub-band & $z_0$ & Pol & $k$  & $\Delta^2_{\text{UL}}$ & $k$ & $\Delta^2_{\text{UL}}$
}
\startdata
Low & 7.1 & E-W & 0.231 & 3.67 $\times 10^4$ & &\\
Low & 7.1 & N-S & 0.27 & 2.70 $\times 10^4$ & 0.154 & 9.3 $\times 10^4$ \\
Mid & 6.8 & E-W & 0.24 & 3.56 $\times 10^4$ & &\\
Mid & 6.8 & N-S & 0.24 & 3.02 $\times 10^4$ & 0.154 & 6.8 $\times 10^4$ \\
High & 6.5 & E-W & 0.20 & 4.70 $\times 10^4$ & &\\
High & 6.5 & N-S & 0.24 & 3.22 $\times 10^4$ & 0.154 & 8.1 $\times 10^4$ \\
\enddata
\end{deluxetable}
